Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2016-10-06 article/article_for_submission.tex
Corrections for the article_for_submission.tex

\institute{Llu\'{i}s Antoni Jim\'{e}nez Rugama \at
              Illinois Institute of Technology, Rettaliata Engineering Center, 10 W 32st, Chicago, IL 60616 \\
\email{ljimene1@hawk.iit.edu}
           \and
           Laurent Gilquin \at
              Inria Grenoble - Rh\^{o}ne-Alpes, Inovall\'{e}e, 655 avenue de l'Europe, 38330 Montbonnot \\
\email{gilquin.laurent@inria.fr}   
}

@@

An inherent practical problem of this estimation is how to quantify the number of model evaluations to ensure that estimates satisfy a desired error tolerance. This paper addresses this challenge by proposing a reliable error bound for first-order and total effect Sobol' indices. Starting from the integral formula of the indices, the error bound is defined in terms of the discrete Walsh coefficients of the different integrands.

@@

Let $f$ represent a deterministic numerical model in $[0,1]^d$, $d \geq 1$. Sensitivity measures, also known as Sobol' indices, are used to assess which inputs of $f$ are influential for the output. The normalized indices are scalars between $0$ and $1$ whose values are interpreted as follows: the closer to $1$ the more influential the index. Alternatively, they can be interpreted as the percentage of the variance explained by the inputs. Among all Sobol' indices one can distinguish \emph{first-order} and \emph{total effect} indices. The first measure the effect of a single input, while the second measure this same effect and includes all its interactions with other inputs.

@@

A practical problem concerning the use of these methods is how to quantify the number of model evaluations to ensure that Sobol' estimates are accurate enough. This article addresses this challenge by proposing a reliable error bound for Sobol' indices based on digital sequences. The error bound is defined in terms of the discrete Walsh coefficients of the integrands involved in the Sobol' indices definition. We propose a sequential estimation procedure of Sobol' indices using the error bound as our stopping criterion. The procedure operates under the assumption that all integrands lie inside a particular cone of functions (see \cite{HicJim}).

Firstly, section \ref{sec:2} introduces Sobol' indices and reviews both Saltelli's strategy to estimate first-order and total effect Sobol' indices, and the replication procedure. Our main contribution is detailed in  Section \ref{sec:3}. There, we review the construction of the error bound proposed in \cite{HicJim} for the estimation of integrals based on digital sequences, and then we generalize it for Sobol' indices. Section \ref{sec:4} is devoted to analyze the cost in terms of model evaluations of our sequential estimation algorithm. It combines the error bound in Section \ref{sec:3} and either one of the two estimation procedures of Section \ref{sec:2}. We also discuss a potential improvement to estimate small first-order indices according to \cite{Owen}. Finally, examples and illustrations of our procedure are presented in Section \ref{sec:5}.

@@

\subsection{Definition of Sobol' indices}
\label{sec:2.1}
%We adopt the same notations introduced by Owen in \cite{Owen}. 
Denote by $\vx=(x_1,\dots,x_d)$ the vector of inputs of\\$f\in \mathbb{L}^2(\cube)$, and $\mathcal{D}=\{1,\dots,d\}$ the set of dimension indexes. %The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality. $\vx_u$ represents a point in $[0,1]^{|u|}$ with components $x_j, j \in u$. Given two points $\vx$ and $\vx'$, the hybrid point $\vw=(\vx_u:{\vx'}_{-u})$ is defined as $w_j=x_j$ if $j \in u$ and $w_j={x'}_j$ if $j \notin u$.% and denote by $\mu$ and $\sigma^2$ the mean $\int_{\cube}f(\vx)d{\vx}$ and variance $\int_{\cube}(f(\vx)-\mu)^2d{\vx}$ of $f$.

The uncertainty on $\vx$ is modeled by a uniform random vector, namely $\vx \iid \mathcal{U}(\cube)$. The Hoeffding decomposition \cite{Hoeffding,Sobol'} of $f$ is:
\begin{equation}
f(\vx)=f_{\varnothing}+\sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} f_u(\vx),
\label{anova}
\end{equation}
where:
\begin{align*}
f_{\varnothing} &= \mathbb{E}[f(\vx)]= \mu, \\
f_u(\vx) &= \int_{[0,1]^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).
\end{align*}
Due to orthogonality, the variance of equation \eqref{anova} leads to the variance decomposition of $f$:
\[ \sigma^2 = \mathrm{Var}[f(\vx)] = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1]^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
From this decomposition, one can express the following two quantities:
\[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad
\ov{$\tau$}_u^2 = \sum \limits_{v \cap u \neq \varnothing} \sigma_v^2, \qquad u \subsetneq \mathcal{D}.\]

These two quantities $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ measure the importance of variables $\vx_u$. $\underline{\tau}_u^2$ quantifies the main effect of $\vx_u$, that is the effect of all interactions between variables in $\vx_u$, and $\ov{$\tau$}_u^2$ quantifies the main effect of $\vx_u$ plus the effect of all interactions between variables in $\vx_u$ and variables in $\vx_{-u}$.

$\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ satisfy the following relations: $ 0 \leq  \underline{\tau}_u^2 \leq \ov{$\tau$}_u^2$ and $\underline{\tau}_u^2 = \sigma^2 - \ov{$\tau$}_{-u}^2$. These two measures are commonly found in the literature in their normalized form: $\underline{S}_u = \underline{\tau}_u^2 / \sigma^2$ is the closed $|u|$-order Sobol' index for inputs $u$, while $\ov{$S$}_u = \ov{$\tau$}_u^2 / \sigma^2$ is the total effect Sobol' index of order $|u|$.
\bigskip

@@

\subsection{Estimation of Sobol' indices}
\label{sec:2.2}
In this section we review two Monte Carlo procedures for the estimation of Sobol' indices. A design is a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ where each point is obtained by sampling each variable $x_j$ $n$ times. Each row of the design is a point $\vx_i$ in $[0,1]^d$ and each column of the design refers to a variable $x_j$. Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid \mathcal{U}([0,1]^{2d})$. One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
\begin{align}
\label{first.order.est}
\widehat{\underline{\tau}_u^2} &= \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_i)-f(\vx_{i,u}:{\vx'}_{i,-u})\right)f(\vx'_i),\\
\label{total.effect.est}
\widehat{\ov{$\tau$}_u^2} &= \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
\end{align}
using for $\sigma^2$:
\begin{equation}
 \widehat{\sigma}^2 = \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i)^2 - \widehat{\mu}^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i).
\label{mu.est}
\end{equation}
Then, the Sobol' indices estimators are:
\begin{equation}
\widehat{\underline{S}}_u = \widehat{\underline{\tau}_u^2} / \widehat{\sigma}^2, \qquad
\widehat{\overline{S}}_u = \widehat{\overline{\tau}_u^2} / \widehat{\sigma}^2.
\label{common.sobol.est}
\end{equation}
Using this method, the estimation of a single pair ($\widehat{\underline{S}}_u$, $\widehat{\overline{S}}_u$) requires $3n$ evaluations of the model $f$. Thus, for all first order and total effect indices, one would need $3nd$ model evaluations. Using a combinatorial formalism, in \cite{Saltelli} Saltelli proposes the following estimation strategy:
\begin{theorem}
\label{saltelli.theorem}
The $d+2$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allow to estimate all first-order and total effect Sobol' indices of order 1 at a cost of $n(d+2)$ evaluations of the model.
\end{theorem}
The main idea of the theorem is that there is no need to reevaluate $f({\vx}_i)$ and $f({\vx'}_i)$ for each $u$. Hence, we can simply evaluate $f({\vx}_i)$ $n$ times, $f({\vx'}_i)$ $n$ times, and $f(\vx_{i,u}:{\vx'}_{i,-u})$ $nd$ times, which accounts for the $n(d+2)$ evaluations.

@@

A more efficient alternative to evaluate all first-order indices was proposed in \cite{Mara} and only requires $2n$ model evaluations. This alternative relies on the construction of two replicated designs. The notion of replicated designs was first introduced by McKay through its replicated Latin Hypercubes in \cite{McKay}. In order to apply this definition to other types of points, in \cite{GJAHMP} we generalized this notion to:
\begin{definition}
\label{rep.designs}
Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in
$[0,1]^{d}$. Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. ${\mathcal{P}'}^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if for any $u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1]^a$. We define by $\pi_u$ the permutation that rearranges the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$.
\end{definition}
The method introduced in \cite{Mara} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$. The key point of this method is to use the permutations resulting from the structure of the two replicated designs to mimic the hybrid points in equation (\ref{first.order.est}).

More precisely, let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two replicated designs of order $1$. Denote by $\{y_i\}_{i=0}^{n-1}=$\\$\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{y'_i\}_{i=0}^{n-1}=\{f({\vx'}_i)\}_{i=0}^{n-1}$ the two sets of model evaluations obtained with $\mathcal{P}$ and $\mathcal{P}'$. From Definition \ref{rep.designs}, we know that ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$. Then,
\begin{align*}
y'_{\pi_u(i)}&= f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u}) \\
&= f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u}).
\end{align*}
Hence, each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) by using $y'_{\pi_u(i)}$ instead of $f(\vx_{i,u}:{\vx'}_{i,-u})$ without requiring further model evaluations for each $u$. This estimation method has been deeply studied and generalized in Tissot et al. \cite{Tissot} to the case of closed second-order indices. In the following we will refer to this method as the replication procedure.

@@

Additional sequential procedures are the replicated procedure and McKay's procedure respectively proposed in \cite{Gilquin.rec} and \cite{Tong}. Nevertheless, in those two cases, the stopping criterion is a quantity of interest purely empirical, built directly upon the estimates. Such stopping criteria often involve hyper-parameters difficult to tweak but more importantly, fail to guarantee any error bound on the estimates.

@@

The description of the error bound is introduced in the following section and our sequential procedure is detailed in section \ref{sec:4}.

@@

Therefore, considering the Walsh decomposition of any $f\in \mathbb{L}^2([0,1]^d)$: \[
f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx), \]
and,
\[ I = \int_{\cube} f(\vx)\,d\vx,\]
property \eqref{basis_integ_prop} leads to
\begin{align}
\nonumber
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} &=
\absolute{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)}, \\
\nonumber
&= \absolute{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}} \\
& \leq \sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\absolute{\hf_{\vk}}. \label{3.1.err_bound}
\end{align}
Based on the size of $\absolute{\hf_{\vk}}$ and the structure of dual nets \eqref{dual_net_structure}, in \cite[Sec. 4.1]{HicJim} we proposed an ordering of the wave-numbers $\vk(\cdot):\naturals_0\rightarrow\naturals_0^d$. Defining $\hf_{\kappa}=\hf_{\vk(\kappa)}$, the error bound \eqref{3.1.err_bound} becomes,
\begin{equation}
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
\end{equation}
Nonetheless, because the knowledge of the Walsh coefficients $\hf_{\kappa}$ is not assumed, we will estimate them using the fast transform obtained with the precomputed function values, and refer to them as $\tf_{m,\kappa}$,
\[
\tf_{m,\kappa}=\tf_{m,\vk(\kappa)}=\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)\overline{\varphi_{\vk(\kappa)}(\vx)}.
\]
Note that for function values evaluated at $\mathcal{P}_m$, one only generates $b^m$ discrete Walsh coefficients $\tf_{m,\kappa}$.

@@

Details concerning the algorithm, the mapping of the wavenumber space, or the meaning and properties of $\cc$, are provided in \cite{HicJim}.

@@

\subsection{Extension to Sobol' indices}
\label{sec:3.2}
The idea here is to extend the definition of the error bound (\ref{errbd}) to Sobol' indices. To do so, we consider the two integral formulas of the first-order and total effect Sobol' indices:
%\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
%In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
\begin{align*}
\underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d}} \left(f(\vx)-
f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\ 
\underline{S}_u(\vI) & = \frac{I_1}{I_3-(I_4)^2}, \\
\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx_u d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\
\overline{S}_u(\vI) & = \frac{I_2}{I_3-(I_4)^2},
\end{align*}
where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values. $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$. If we estimate $\vI$ by $\widehat{\vI}$ with vector of error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$,\\ $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.

>>>>

\institute{Llu\'{i}s Antoni Jim\'{e}nez Rugama \at
              Illinois Institute of Technology, Rettaliata Engineering Center, Room 208, 10 W 32st, Chicago, IL 60616 \\
\email{ljimene1@hawk.iit.edu}
           \and
           Laurent Gilquin \at
              Inria Grenoble - Rh\^{o}ne-Alpes, Inovall\'{e}e, 655 avenue de l'Europe, 38330 Montbonnot \\
\email{gilquin.laurent@inria.fr}   
}

@@

An inherent practical problem of this estimation is how to quantify the number of model evaluations needed to ensure that estimates satisfy a desired error tolerance. This paper addresses this challenge by proposing a reliable error bound for first-order and total effect Sobol' indices. Starting from the integral formula of the indices, the error bound is defined in terms of the discrete Walsh coefficients of the different integrands.

@@

Let $f$ represent a deterministic numerical model in $[0,1]^d$, $d \geq 1$. Sensitivity measures, also known as Sobol' indices, are used to assess which inputs of $f$ are influential for the output. The normalized indices are scalars between $0$ and $1$ whose values are interpreted as follows: the closer to $1$ the more influential the index. Alternatively, they can be interpreted as the percentage of the variance explained by the inputs. Among all Sobol' indices one can distinguish \emph{first-order} and \emph{total effect} indices. The first measure the effect of a single input, while the second measure the effect of a single input plus all its interactions with other inputs.

@@

A practical problem concerning the use of these methods is how to quantify the number of model evaluations required to ensure that Sobol' estimates are accurate enough. This article addresses this challenge by proposing a reliable error bound for Sobol' indices based on digital sequences. The error bound is defined in terms of the discrete Walsh coefficients of the integrands involved in the Sobol' indices definition. We propose a sequential estimation procedure of Sobol' indices using the error bound as our stopping criterion. The procedure operates under the assumption that all integrands lie inside a particular cone of functions (see \cite{HicJim}).

Firstly, Section \ref{sec:2} introduces Sobol' indices and reviews both Saltelli's strategy to estimate first-order and total effect Sobol' indices, and the replication procedure. Our main contribution is detailed in  Section \ref{sec:3}. There, we review the construction of the error bound proposed in \cite{HicJim} for the estimation of integrals based on digital sequences, and then we generalize it for Sobol' indices. Section \ref{sec:4} is devoted to analyze the cost in terms of model evaluations of our sequential estimation algorithm. It combines the error bound in Section \ref{sec:3} and either one of the two estimation procedures of Section \ref{sec:2}. We also discuss a potential improvement to estimate small first-order indices according to \cite{Owen}. Finally, examples and illustrations of our procedure are presented in Section \ref{sec:5}.

@@

\subsection{Definition of Sobol' indices}
\label{sec:2.1}
%We adopt the same notations introduced by Owen in \cite{Owen}. 
Denote by $\vx=(x_1,\dots,x_d)$ the vector of inputs of $f$. We assume that $f$ is in some subset of $\in \mathbb{L}^2(\cube)$ for which $f(\vx)$ is defined for all $\vx\in\cube$, and $\mathcal{D}=\{1,\dots,d\}$ the set of dimension indexes. %The uncertainty on $\vx$ is modeled by a random vector that we suppose uniformly distributed on $\cube$.
Let $u$ be a subset of $\mathcal{D}$, $-u$ its complement and $|u|$ its cardinality. Then, $\vx_u$ represents a point in $[0,1]^{|u|}$ with components $x_j, j \in u$. Given two points $\vx$ and $\vx'$, the hybrid point $\vw=(\vx_u:{\vx'}_{-u})$ is defined as $w_j=x_j$ if $j \in u$ and $w_j=x'_j$ if $j \notin u$.% and denote by $\mu$ and $\sigma^2$ the mean $\int_{\cube}f(\vx)d{\vx}$ and variance $\int_{\cube}(f(\vx)-\mu)^2d{\vx}$ of $f$.

The uncertainty on $\vx$ is modeled by a uniform random vector, namely $\vx \iid \mathcal{U}(\cube)$. The Hoeffding decomposition \cite{Hoeffding,Sobol'} of $f$ is:
\begin{equation}
f(\vx)=f_{\varnothing}+\sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} f_u(\vx),
\label{anova}
\end{equation}
where:
\begin{align*}
f_{\varnothing} &= \mathbb{E}[f(\vx)]= \mu, \\
f_u(\vx) &= \int_{[0,1]^{|u|}} f(\vx) d{\vx}_{-u} - \sum \limits_{v \subset u} f_v(\vx).
\end{align*}
Due to orthogonality, the variance of equation \eqref{anova} leads to the variance decomposition of $f$:
\[ \sigma^2 = \mathrm{Var}[f(\vx)] = \sum \limits_{u \subseteq \mathcal{D}, u \neq \varnothing} \sigma_u^2, \ \text{ with } \ \sigma_u^2=\int_{[0,1]^{|u|}} f_u(\vx)^2 d{\vx_u}.\]
From this decomposition, one can define the following two quantities:
\[\underline{\tau}_u^2 = \sum \limits_{v \subseteq u} \sigma_v^2, \qquad
\ov{$\tau$}_u^2 = \sum \limits_{v \cap u \neq \varnothing} \sigma_v^2, \qquad u \subsetneq \mathcal{D}.\]

These two quantities $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ measure the importance of variables $\vx_u$: $\underline{\tau}_u^2$ quantifies the main effect of $\vx_u$, that is the effect of all interactions between variables in $\vx_u$, and $\ov{$\tau$}_u^2$ quantifies the main effect of $\vx_u$ plus the effect of all interactions between variables in $\vx_u$ and variables in $\vx_{-u}$.

Both $\underline{\tau}_u^2$ and $\ov{$\tau$}_u^2$ satisfy the following relations: $ 0 \leq  \underline{\tau}_u^2 \leq \ov{$\tau$}_u^2$ and $\underline{\tau}_u^2 = \sigma^2 - \ov{$\tau$}_{-u}^2$. These two measures are commonly found in the literature in their normalized form: $\underline{S}_u = \underline{\tau}_u^2 / \sigma^2$ is the closed $|u|$-order Sobol' index for inputs $u$, while $\ov{$S$}_u = \ov{$\tau$}_u^2 / \sigma^2$ is the total effect Sobol' index of order $|u|$.
\bigskip

@@

\subsection{Estimation of Sobol' indices}
\label{sec:2.2}
In this section we review two Monte Carlo procedures for the estimation of Sobol' indices. A design is a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ where each point is obtained by sampling each variable $x_j$ $n$ times. Each row of the design is a point $\vx_i$ in $[0,1]^d$ and each column of the design refers to samples of a variable $x_j$. Consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P'}=\{{\vx'}_i\}_{i=0}^{n-1}$ two designs where $(\vx_i,{\vx'}_i) \iid \mathcal{U}([0,1]^{2d})$. One way to estimate the two quantities (\ref{first.order}) and (\ref{total.effect}) is via:
\begin{align}
\label{first.order.est}
\widehat{\underline{\tau}_u^2} &= \frac{1}{n} \sum \limits_{i=0}^{n-1} \left(f(\vx_i)-f(\vx_{i,u}:{\vx'}_{i,-u})\right)f(\vx'_i),\\
\label{total.effect.est}
\widehat{\ov{$\tau$}_u^2} &= \frac{1}{2n} \sum \limits_{i=0}^{n-1} (f({\vx'}_i) - f(\vx_{i,u}:{\vx'}_{i,-u}))^2, \qquad u \in \mathcal{D},
\end{align}
using for $\sigma^2$:
\begin{equation}
 \widehat{\sigma}^2 = \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i)^2 - \widehat{\mu}^2, \text{ with } \ \widehat{\mu} =  \frac{1}{n} \sum \limits_{i=0}^{n-1} f(\vx_i).
\label{mu.est}
\end{equation}
Then, the Sobol' indices estimators are:
\begin{equation}
\widehat{\underline{S}}_u = \widehat{\underline{\tau}_u^2} / \widehat{\sigma}^2, \qquad
\widehat{\overline{S}}_u = \widehat{\overline{\tau}_u^2} / \widehat{\sigma}^2.
\label{common.sobol.est}
\end{equation}
Using this method, the estimation of a single pair ($\widehat{\underline{S}}_u$, $\widehat{\overline{S}}_u$) requires $3n$ evaluations of the model $f$. Thus, for all first order and total effect indices, one would need $3nd$ model evaluations. Using a combinatorial formalism, in \cite{Saltelli} Saltelli proposes the following estimation strategy:
\begin{theorem}
\label{saltelli.theorem}
The $d+2$ designs $\{\vx_{i,u}:{\vx'}_{i,-u}\}_{i=0}^{n-1}$ constructed for $u \in \{\varnothing,\{1\},\dots,$ $\{d\},\mathcal{D}\}$ allow to estimate all first-order and total effect Sobol' indices of order 1 at a cost of $n(d+2)$ evaluations of the model.
\end{theorem}
The main idea of the theorem is that there is no need to reevaluate $f({\vx}_i)$ and $f({\vx'}_i)$ for each $u$. Hence, we can simply evaluate $f({\vx}_i)$ $n$ times, $f({\vx'}_i)$ $n$ times, and $f(\vx_{i,u}:{\vx'}_{i,-u})$ $nd$ times, which accounts for the $n(d+2)$ evaluations.

@@

A more efficient alternative to evaluate all first-order indices was proposed in \cite{Mara} and only requires $2n$ model evaluations. This alternative relies on the construction of two replicated designs. The notion of replicated designs was first introduced by McKay through his replicated Latin Hypercubes in \cite{McKay}. In order to apply this definition to other types of points, in \cite{GJAHMP} we generalized this notion to the following.
\begin{definition}
\label{rep.designs}
Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in
$[0,1]^{d}$. Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. ${\mathcal{P}'}^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if for any $u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1]^a$. We define by $\pi_u$ the permutation that rearranges the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$.
\end{definition}
The method introduced in \cite{Mara} allows to estimate all first-order Sobol' indices with only two replicated designs of order $1$. The key point of this method is to use the permutations resulting from the structure of the two replicated designs to mimic the hybrid points in equation (\ref{first.order.est}).

More precisely, let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two replicated designs of order $1$. Denote by $\{y_i\}_{i=0}^{n-1}=$\\$\{f(\vx_i)\}_{i=0}^{n-1}$ and $\{y'_i\}_{i=0}^{n-1}=\{f({\vx'}_i)\}_{i=0}^{n-1}$ the two sets of model evaluations obtained with $\mathcal{P}$ and $\mathcal{P}'$. From Definition \ref{rep.designs}, we know that ${\vx'}_{\pi_u(i),u}={\vx}_{i,u}$. Then,
\begin{align*}
y'_{\pi_u(i)}&= f(\vx'_{\pi_u(i),u}:{\vx'}_{\pi_u(i),-u}) \\
&= f(\vx_{i,u}:{\vx'}_{\pi_u(i),-u}).
\end{align*}
Hence, each $\underline{\tau}^2_u$ can be estimated via formula (\ref{first.order.est}) by using $y'_{\pi_u(i)}$ instead of $f(\vx_{i,u}:{\vx'}_{i,-u})$ without requiring further model evaluations for each $u$. This estimation method has been studied deeply and generalized in Tissot et al. \cite{Tissot} to the case of closed second-order indices. In the following we will refer to this method as the replication procedure.

@@

Additional sequential procedures are the replicated procedure and McKay's procedure respectively proposed in \cite{Gilquin.rec} and \cite{Tong}. Nevertheless, in those two cases, the stopping criterion is a purely empirical quantity of interest, built directly upon the estimates. Such stopping criteria often involve hyper-parameters that are difficult to tweak but more importantly, fail to guarantee any error bound on the estimates.

@@

The description of the error bound is introduced in the following section and our sequential procedure is detailed in Section \ref{sec:4}.

@@

Therefore, considering the Walsh decomposition of any $f\in \mathbb{L}^2([0,1]^d)$: \[
f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx), \]
and,
\[ I = \int_{\cube} f(\vx)\,d\vx,\]
property \eqref{basis_integ_prop} leads to
\begin{align}
\nonumber
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} &=
\absolute{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)}, \\
\nonumber
&= \absolute{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}} \\
& \leq \sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\absolute{\hf_{\vk}}. \label{3.1.err_bound}
\end{align}
Based on the size of $\absolute{\hf_{\vk}}$ and the structure of dual nets \eqref{dual_net_structure}, in \cite[Sec. 4.1]{HicJim} we proposed an ordering of the \emph{wavenumbers} $\vk(\cdot):\naturals_0\rightarrow\naturals_0^d$. Defining $\hf_{\kappa}=\hf_{\vk(\kappa)}$, the error bound \eqref{3.1.err_bound} becomes,
\begin{equation}
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
\end{equation}
Nonetheless, because the knowledge of the Walsh coefficients $\hf_{\kappa}$ is not assumed, we will estimate them using the fast transform obtained with the precomputed function values, and refer to them as $\tf_{m,\kappa}$,
\[
\tf_{m,\kappa}=\tf_{m,\vk(\kappa)}=\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)\overline{\varphi_{\vk(\kappa)}(\vx)}.
\]
Note that for function values evaluated at $\mathcal{P}_m$, one only generates $b^m$ discrete Walsh coefficients $\tf_{m,\kappa}$.

@@

Details concerning the algorithm, the mapping of the \emph{wavenumber} space, or the meaning and properties of $\cc$, are provided in \cite{HicJim}.

@@

\subsection{Extension to Sobol' indices}
\label{sec:3.2}
The idea here is to extend the definition of the error bound (\ref{errbd}) to Sobol' indices. To achieve this goal, we consider the two integral formulas of the first-order and total effect Sobol' indices with $|u|=1$:
%\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
%In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
\begin{align*}
\underline{S}_u(\vI) & = \frac{\int_{[0,1)^{2d}} \left(f(\vx)-
f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\ 
\underline{S}_u(\vI) & = \frac{I_1}{I_3-(I_4)^2}, \\
\overline{S}_u(\vI) & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx_u d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\left(\int_{[0,1)^{d}} f(\vx) d{\vx}\right)^2}, \\
\overline{S}_u(\vI) & = \frac{I_2}{I_3-(I_4)^2},
\end{align*}
where $\vI=(I_1,I_2,I_3,I_4)$ is a vector of integral values. Indices $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ are defined as functions over the vector $\vI$. If we estimate $\vI$ by $\widehat{\vI}$ with vector of error bounds $\varepsilon_{\widehat{\vI}}=(\epsilon_{\widehat{I}_1},\epsilon_{\widehat{I}_2},\epsilon_{\widehat{I}_3}$,\\ $\epsilon_{\widehat{I}_4})$ according to (\ref{errbd}), we know that $\vI\in B_{\varepsilon_{\widehat{\vI}}}(\widehat{\vI})=[\widehat{\vI}-\varepsilon_{\widehat{\vI}},\widehat{\vI}+\varepsilon_{\widehat{\vI}} ]$.
